Online (Bandit) Policy Selection for EASY-Backfilling

### 2017-03-30 paper/src/paper.tex
artifact change
small fixes to the artifacts.

{\small
\begin{itemize}
  \item {\bf algorithm: Scheduling Simulation Workflow}
  \item {\bf program: Ocaml, R, Bash, Zymake(all sources and dependencies included)}
  \item {\bf compilation: Ocaml 4.02.3, GNU bash version 4.4.5(1)-release, R version 3.3.2}
  \item {\bf transformations: Patched nix standard environment.}
  \item {\bf binary: Most binaries are cached by Nix channels.}
  \item {\bf data set: Traces from the parallel workload archive, included.}
  \item {\bf run-time environment: Nixpkgs 17.03}
  \item {\bf hardware: Dell PowerEdge R730}
  \item {\bf output: Files}
  \item {\bf experiment workflow: \lstinline[basicstyle=\ttfamily\color{blue}]|zymakefile|, see below}
  \item {\bf publicly available?: Yes}
\end{itemize}
}

@@

@@

All the software dependencies of our code
Managed by Nix.

\dirtree{%
.1 root .
.2 zymakefile .
.2 default.nix .
.2 pkgs .
.2 gz .
.3 ANL-Intrepid.swf.gz .
.3 CEA-Curie.swf.gz .
.3 CTC-SP2.swf.gz .
.3 KTH-SP2.swf.gz .
.3 SDSC-BLUE.swf.gz .
.3 SDSC-SP2.swf.gz .
.3 UniLu-Gaia.swf.gz .
.2 misc .
.3 strongvisu .
.3 visu .
.2 ocst .
.2 paper .
}

@@

From Swf Archive. Cached.

@@

nix-build

@@

o/zymakefile/pdfs

@@

modify zymakefile

>>>>

{\small
\begin{itemize}
  \item {\bf algorithm: Scheduling Simulation Workflow}
  \item {\bf program: Ocaml, R, Bash, Zymake(all sources and dependencies included)}
  \item {\bf compilation: Ocaml 4.02.3, GNU bash version 4.4.5(1)-release, R version 3.3.2}
  \item {\bf transformations: Patched nix standard environment.}
  \item {\bf binary: Most binaries are cached by Nix channels.}
  \item {\bf data set: Traces from the parallel workload archive, included.}
  \item {\bf run-time environment: Nixpkgs 17.03}
  \item {\bf hardware: Dell PowerEdge R730}
  \item {\bf output: Files}
  \item {\bf experiment workflow: \lstinline[basicstyle=\ttfamily\color{blue}]|zymakefile|, see below}
  \item {\bf publicly available?: Open-Sourced under the ISC~\cite{isc} license.}
\end{itemize}
}

@@

\textbf{one-liner : replication}

@@

All the software dependencies of our experiments are automatically managed by Nix.

@@

All data from this paper was obtained from the Swf Parallel Workloads
Archive~\cite{Feitelson20142967}. The data is cached in gzipped format in the
persistent archive associated with this workflow, should the Parallel
Workdloads Archive become unavailable.

@@

The experiment dependencies are loaded into the environment by the
\lstinline[basicstyle=\ttfamily]|nix-build| command.

Nevertheless, the reader interested in using the tools outside the workflow can
obtain an environment by running the
\lstinline[basicstyle=\ttfamily]|nix-shell| command:

\begin{lstlisting}
nix-shell (fetchTarball ...)
\end{lstlisting}

Or alternatively, if the user is at the root of the extracted archive:

\begin{lstlisting}
nix-shell -A banditSelection
\end{lstlisting}

This allows to use the following command-line tools:

\begin{itemize}

  \item[ocs] The scheduling simulator used in the experiments. Use
    \lstinline[basicstyle=\ttfamily]|ocs --help| to see all available options.

  \item[ocs-sampler] The workload resampler used in the experiments. Use
    \lstinline[basicstyle=\ttfamily]|ocs-sampler --help| for usage.

  \item[zymake] The zymake~\cite{zymake} tool.
    The workflow can be executed in the current environment in parallel
    via \lstinline[basicstyle=\ttfamily]|zymake -l localhost zymakefile|.

@@

All resulting figures will be situated in the simlinked folder named
\lstinline[basicstyle=\ttfamily\color{blue}]|result| positionned at the root of
the archive.

@@

Readers interested with modifying the experiments can obtain the zenodo archive at \url{https://...}

The experiments are replicated with the same procedure as before, this time invoking
the build command with the local folder:

\begin{lstlisting}
nix-build -A banditSelection
\end{lstlisting}

The file tree has the following structure:

\dirtree{%
  .1 root .
.2 zymakefile \textcolor{brown}{Zymake workflow} .
.2 default.nix \textcolor{brown}{Nix packaging} .
.2 pkgs/ \textcolor{brown}{Nix packaging} .
.2 gz/ \textcolor{brown}{Data archive} .
.3 ANL-Intrepid.swf.gz .
.3 $\cdots$ .
.2 misc/ \textcolor{brown}{Visualization and filtering code} .
.2 ocst/ \textcolor{brown}{Simulator Code} .
.2 paper/ \textcolor{brown}{This article.} .
}

Most simple workflow modifications (using different traces, changing the sample
sizes) can be obtained by modifying the
\lstinline[basicstyle=\ttfamily\color{blue}]|zymakefile|. For modification
